---
title: "Analyses"
output: 
  github_document:
  toc: true
date: "11/06/2022"
author: Young Ha Suh, ys757@cornell.edu; Vanya Rohwer, vgr7@cornell.edu
editor_options: 
  chunk_output_type: console
---

Libraries
```{r}
# figures
library(ggpubr)
library(ggpmisc)
library(cowplot)
#analyses
library(pavo)
library(lme4)
library(DHARMa)
```
  
Load data
```{r}
alldat.orn <- readRDS("alldat.orn.rds")
alldat.blk <- readRDS("alldat.blk.rds")
```

# Colorimetric variables
List of variables of interest (from Pavo package; references available there)
 - `B1`: total brightness; sum of relative reflectance over entire spectral range (area under the curve) 
 - `S9`: carotenoid chroma; (R700 - R450)/R700 
 - `H3`: hue/wavelength at Rmid; sensitive to noisy spectra

### Compare boxplots across specimen categories
Orange patches
```{r Boxplot across specimens - orange}
dat <- alldat.orn

plot(B1 ~ cat, data = dat, ylab = "Total brightness (B1)", xlab = "Specimen category")
plot(S9 ~ cat, data = dat, ylab = "Carotenoid chroma (S9)", xlab = "Specimen category")
plot(H3 ~ cat, data = dat, ylab = "Hue (H3)", xlab = "Specimen category")
```

Black patchess 
```{r Boxplot across specimens - black}
dat <- alldat.blk
plot(B1 ~ cat, data = dat, ylab = "Total brightness (B1)", xlab = "Specimen category")
```

### Check data 
## Histograms

Normality
```{r qqPlots}
# Oranges
qqPlot(alldat.orn$B1)
qqPlot(alldat.orn$B2)
qqPlot(alldat.orn$S9)
qqPlot(alldat.orn$H3)

# Black
qqPlot(alldat.blk$B1)
```

Compare variances
```{r}
table(alldat.orn[which(alldat.orn$sp == "Bull"),]$cat)

bullchk <- alldat.orn[which(alldat.orn$cat == "Bull_mod" | alldat.orn$cat == "Bull_hist"),]
baltchk <- alldat.orn[which(alldat.orn$cat == "Balt_mod" | alldat.orn$cat == "Balt_hist"),]

# F-test
res <- var.test(B1 ~ cat, data = bullchk)
res 
#F = 0.93703, num df = 19, denom df = 19, p-value = 0.8888
#there is no significant difference between the two variances

res <- var.test(S9 ~ cat, data = bullchk)
res 
#F = 2.3205, num df = 19, denom df = 19, p-value = 0.07421

res <- var.test(H3 ~ cat, data = bullchk)
res 
#F = 2.4874, num df = 19, denom df = 19, p-value = 0.05384

#############
# Baltimores
res1 <- var.test(B1 ~ cat, data = baltchk)
res1
#F = 0.87801, num df = 19, denom df = 18, p-value = 0.7793

res1 <- var.test(S9 ~ cat, data = baltchk)
res1
#F = 5.7141, num df = 19, denom df = 18, p-value = 0.0005181 -> ????????????? 

res1 <- var.test(H3 ~ cat, data = baltchk)
res1
#F = 0.76303, num df = 19, denom df = 18, p-value = 0.5635


################
# Same for black patch
bullchk1 <- alldat.blk[which(alldat.blk$cat == "Bull_mod" | alldat.blk$cat == "Bull_hist"),]
baltchk1 <- alldat.blk[which(alldat.blk$cat == "Balt_mod" | alldat.blk$cat == "Balt_hist"),]

# F-test
res <- var.test(B1 ~ cat, data = bullchk1)
res  #F = 0.5821, num df = 19, denom df = 19, p-value = 0.2473
res <- var.test(B1 ~ cat, data = baltchk1)
res  #F = 0.45773, num df = 19, denom df = 18, p-value = 0.09953


##############
# Use Levene Test
library(car)
leveneTest(B1 ~ cat, data = bullchk) #0.001 0.9754
leveneTest(S9 ~ cat, data = bullchk) #5.8549 0.02043 *
leveneTest(H3 ~ cat, data = bullchk) #4.0309 0.05182 .
leveneTest(B1 ~ cat, data = baltchk) #0.0336 0.8555
leveneTest(S9 ~ cat, data = baltchk) #3.9957  0.053 .
leveneTest(H3 ~ cat, data = baltchk) #0.0034 0.9538

leveneTest(B1 ~ cat, data = bullchk1) # 1.052 0.3115
leveneTest(B1 ~ cat, data = baltchk1) #1.1375 0.2931
```

Based on variances, use appropriate comparative tests:
```{r}
# Bullock's
t.test(B1 ~ cat, data = bullchk) #t = 1.4878, df = 37.96, p-value = 0.1451
wilcox.test(S9 ~ cat, data = bullchk) #W = 61, p-value = 7.938e-05
t.test(H3 ~ cat, data = bullchk) #t = -4.8794, df = 32.151, p-value = 2.791e-05

# Baltimore
t.test(B1 ~ cat, data = baltchk) #t = 1.2933, df = 36.496, p-value = 0.204
wilcox.test(S9 ~ cat, data = baltchk) #W = 161, p-value = 0.4276
t.test(H3 ~ cat, data = baltchk) #t = 2.7705, df = 35.755, p-value = 0.008821

# black patches
wilcox.test(B1 ~ cat, data = bullchk1) #W = 127, p-value = 0.04909
wilcox.test(B1 ~ cat, data = baltchk1) #W = 83, p-value = 0.002121
```


<br>

# Statistical analyses
## H1. Have specimens faded over time? 
To test for specimen fauxing, look at colorimetric measures over time.

### 1. Orange patches over time

Check brightness, carotenoid chroma, hue

1) Brightness
```{r Orange - brightness x date, message = FALSE}
# Both species
lm_orn_both_b1 <- lm(B1 ~ date, data = alldat.orn)
summary(lm_orn_both_b1)
simulationOutput <- simulateResiduals(fittedModel = lm_orn_both_b1, plot = F)
plot(simulationOutput)

# Bullock's
lm_orn_BU_b1 <- lm(B1 ~ date, data = alldat.orn[which(alldat.orn$sp == "Bull"),])
summary(lm_orn_BU_b1)
simulationOutput <- simulateResiduals(fittedModel = lm_orn_BU_b1, plot = F)
plot(simulationOutput)

# Baltimore
lm_orn_BA_b1 <- lm(B1 ~ date, data = alldat.orn[which(alldat.orn$sp == "Balt"),])
summary(lm_orn_BA_b1)
simulationOutput <- simulateResiduals(fittedModel = lm_orn_BA_b1, plot = F)
plot(simulationOutput)

# Plot both
ggplot(alldat.orn, aes(x = date, y = B1, shape = spc, color = spc)) +
  geom_point(size = 2) +
  stat_smooth(method = lm, aes(fill = spc), se = T) +
  theme_classic() +
  mytheme +
  stat_fit_glance(method = "lm", label.x = "right", label.y = "bottom",
                        method.args = list(formula = y ~ x), size = 5, 
                        aes(label = sprintf('R^2~"="~%.3f~~italic(p)~"="~%.3f',
                                            stat(..r.squared..), stat(..p.value..))), 
                  parse = TRUE) + 
  labs(title = "Orange patches only", y = "Total brightness (B1)", x = "Collection date", 
       color = "Species", fill = "Species", shape = "Species") +
  scale_color_manual(values = pal1) +
  scale_fill_manual(values = pal1)
```

2) Carotenoid chroma 
```{r Orange - chroma x date, message = FALSE}
# Both species
lm_orn_both_s9 <- lm(S9 ~ date, data = alldat.orn)
summary(lm_orn_both_s9)
simulationOutput <- simulateResiduals(fittedModel = lm_orn_both_s9, plot = F)
plot(simulationOutput)

# Bullock's
lm_orn_BU_s9 <- lm(S9 ~ date, data = alldat.orn[which(alldat.orn$sp == "Bull"),])
summary(lm_orn_BU_s9)

# Baltimore
lm_orn_BA_s9 <- lm(S9 ~ date, data = alldat.orn[which(alldat.orn$sp == "Balt"),])
summary(lm_orn_BA_s9)

# Plot both
ggplot(alldat.orn, aes(x = date, y = S9, shape = spc, color = spc)) +
  geom_point(size = 2) +
  stat_smooth(method = lm, aes(fill = spc), se = T) +
  theme_classic() +
  mytheme +
  stat_fit_glance(method = "lm", label.x = "right", label.y = "bottom",
                        method.args = list(formula = y ~ x), size = 5, 
                        aes(label = sprintf('R^2~"="~%.3f~~italic(p)~"="~%.3f',
                                            stat(..r.squared..), stat(..p.value..))), 
                  parse = TRUE) + 
  labs(title = "Orange patches only", y = "Carotenoid chroma (S9)", x = "Collection date", 
       color = "Species", fill = "Species", shape = "Species") +
  scale_color_manual(values = pal1) +
  scale_fill_manual(values = pal1)
```

3) Hue 
```{r Orange - hue x date, message = FALSE}
# Both species
lm_orn_both_h3 <- lm(H3 ~ date, data = alldat.orn)
summary(lm_orn_both_h3)

# Bullock's
lm_orn_BU_h3 <- lm(H3 ~ date, data = alldat.orn[which(alldat.orn$sp == "Bull"),])
summary(lm_orn_BU_h3)

# Baltimore
lm_orn_BA_h3 <- lm(H3 ~ date, data = alldat.orn[which(alldat.orn$sp == "Balt"),])
summary(lm_orn_BA_h3)

# Plot both
ggplot(alldat.orn, aes(x = date, y = H3, shape = spc, color = spc)) +
  geom_point(size = 2) +
  stat_smooth(method = lm, aes(fill = spc), se = T) +
  theme_classic() +
  mytheme +
  stat_fit_glance(method = "lm", label.x = "right", label.y = "bottom",
                        method.args = list(formula = y ~ x), size = 5, 
                        aes(label = sprintf('R^2~"="~%.3f~~italic(p)~"="~%.3f',
                                            stat(..r.squared..), stat(..p.value..))), 
                  parse = TRUE) + 
  labs(title = "Orange patches only", y = "Hue (H3)", x = "Collection date", 
       color = "Species", fill = "Species", shape = "Species") +
  scale_color_manual(values = pal1) +
  scale_fill_manual(values = pal1)
```

### 2. Black patches over time

Check brightness

```{r Black - brightness x date, message = FALSE}
lm_black <- lm(B1 ~ date, data = alldat.blk)
summary(lm_black)

# plot
ggplot(alldat.blk, aes(x = date, y = B1, shape = spc, color = spc)) +
  geom_point(size = 2) +
  stat_smooth(method = lm, aes(fill = spc), se = T) +
  theme_classic() +
  mytheme +
  stat_fit_glance(method = "lm", label.x = "right", label.y = "bottom",
                        method.args = list(formula = y ~ x), size = 5, 
                        aes(label = sprintf('R^2~"="~%.3f~~italic(p)~"="~%.3f',
                                            stat(..r.squared..), stat(..p.value..))), 
                  parse = TRUE) + 
  labs(title = "Black patches only", y = "Brightness (B1)", x = "Collection date", 
       color = "Species", fill = "Species", shape = "Species") +
  scale_color_manual(values = pal1) +
  scale_fill_manual(values = pal1)
```


<br>

## H2. Have landuse changes affected Bullock's orioles?

Compare reference vs. hybrid zone

```{r H2. Reference vs hybrid zone}
# Select categories for comparison 
compare <- alldat.orn[which(alldat.orn$cat == "Bull_mod" | 
                            alldat.orn$cat == "Bull_hist" | 
                            alldat.orn$cat == "Balt_mod" | 
                            alldat.orn$cat == "Balt_hist"),]

# List for comparisons
comparelist <- list(c("Bull_hist", "Bull_mod"), c("Balt_hist", "Balt_mod"))


############
# for black patches
compare1 <- alldat.blk[which(alldat.blk$cat == "Bull_mod" | 
                             alldat.blk$cat == "Bull_hist" | 
                             alldat.blk$cat == "Balt_mod" | 
                             alldat.blk$cat == "Balt_hist"),]
```


1. Brightness boxplots
```{r compare across bullocks groups - brightness, message = FALSE, warning = FALSE}
b1orn <- ggplot(compare, aes(x = cat, y = B1, fill = sp)) +
  stat_boxplot(aes(x = cat, y = B1), geom = "errorbar", 
               position = position_dodge(width = .75), width = .5) +
  geom_boxplot(outlier.size = 1.5, position = position_dodge(width = .75), col = "black") +
  stat_compare_means(comparisons = comparelist, method = "t.test", label = "p.signif", size = 6) +
  theme_classic()+
  mytheme +
  labs(y = "Total brightness (B1)") +
  scale_fill_manual(values = pal1, name = "Species", 
                    limits = c("Bull", "Balt"), 
                    labels = c(expression(italic("Icterus bullockii")), 
                               expression(italic("Icterus galbula")))) +
  scale_x_discrete(name = "Specimen type", 
                   limits = c("Bull_hist", "Bull_mod", "Balt_hist", "Balt_mod"), 
                   labels = c("Historic", "Contemporary","Historic", "Contemporary")) +
  theme(legend.text.align = 0,
        axis.text.x=element_text(angle=45, vjust = 1, hjust=1))

b1orn

# black
b1blk <- ggplot(compare1, aes(x = cat, y = B1, fill = sp)) +
  stat_boxplot(aes(x = cat, y = B1), geom = "errorbar", 
               position = position_dodge(width = .75), width = .5) +
  geom_boxplot(outlier.size = 1.5, position = position_dodge(width = .75), col = "black") +
  stat_compare_means(comparisons = comparelist, method = "t.test", label = "p.signif", size = 6) + 
  theme_classic()+ 
  mytheme +
  labs(y = "Black plumage brightness (B1)") +
  scale_fill_manual(values = pal1, name = "Species", 
                    limits = c("Bull", "Balt"), 
                    labels = c("Bullock's Oriole", 
                               "Baltimore Oriole")) +
  scale_x_discrete(name = "Specimen type", 
                   limits = c("Bull_hist", "Bull_mod", "Balt_hist", "Balt_mod"), 
                   labels = c("Historic", "Contemporary","Historic", "Contemporary")) +
  theme(legend.text.align = 0) +
  ylim(900,4000)
b1blk

ggsave("Figure4.png", plot=b1blk, width=220, height=125, units="mm", dpi=600, scale=T)
```

2. Chroma
```{r compare across bullocks groups - chroma, message = FALSE, warning = FALSE}
s9orn <- ggplot(compare, aes(x = cat, y = S9, fill = sp)) +
  stat_boxplot(aes(x = cat, y = S9), geom = "errorbar", 
               position = position_dodge(width = .75), width = .5) +
  geom_boxplot(outlier.size = 1.5, position = position_dodge(width = .75), col = "black") +
  stat_compare_means(comparisons = comparelist, method = "t.test", label = "p.signif", size = 6) + 
  theme_classic()+ 
  mytheme +
  labs(y = "Carotenoid chroma (S9)") +
  scale_fill_manual(values = pal1, name = "Species", 
                    limits = c("Bull", "Balt"), 
                    labels = c(expression(italic("Icterus bullockii")), 
                               expression(italic("Icterus galbula")))) +
  scale_x_discrete(name = "Specimen type", 
                   limits = c("Bull_hist", "Bull_mod", "Balt_hist", "Balt_mod"), 
                   labels = c("Historic", "Contemporary","Historic", "Contemporary")) +
  theme(legend.text.align = 0,
        axis.text.x=element_text(angle=45, vjust = 1, hjust=1))
s9orn
```


3. Hue
```{r compare across bullocks groups - hue, message = FALSE, warning = FALSE}
h3orn <- ggplot(compare, aes(x = cat, y = H3, fill = sp)) +
  stat_boxplot(aes(x = cat, y = H3), geom = "errorbar", 
               position = position_dodge(width = .75), width = .5) +
  geom_boxplot(outlier.size = 1.5, position = position_dodge(width = .75), col = "black") +
  stat_compare_means(comparisons = comparelist, method = "t.test", label = "p.signif", size = 6) + 
  theme_classic()+ 
  mytheme +
  labs(y = "Hue (H3)") +
  scale_fill_manual(values = pal1, name = "Species", 
                    limits = c("Bull", "Balt"), 
                    labels = c("Bullock's Oriole", "Baltimore Oriole")) +
  scale_x_discrete(name = "Specimen type", 
                   limits = c("Bull_hist", "Bull_mod", "Balt_hist", "Balt_mod"), 
                   labels = c("Historic", "Contemporary","Historic", "Contemporary")) +
  theme(legend.text.align = 0, legend.position = c(0.7, 0.15), 
        legend.background = element_rect(linetype="solid", colour ="lightgray"),
        axis.text.x=element_text(angle=45, vjust = 1, hjust=1)) +
  ylim(530,573)

h3orn 
```

Plot all three together
```{r compare across bullocks groups - all3, message = FALSE, warning = FALSE}
#########
pg <- plot_grid(
  b1orn + theme(legend.position="none"),
  s9orn + theme(legend.position="none"),
  h3orn,
  align = 'vh',
  labels = c("A", "B", "C"),
  hjust = -1,
  nrow = 1, label_size = 16
)

plot_grid(pg)

ggsave("Figure3.png", plot=last_plot(), width=400, height=150, units="mm", dpi=600, scale=T)
```


<br>

## H3. Are color changes only in the hybrid zone? 

```{r H3 data setup, message = FALSE, warning = FALSE}
# Set a new variable indicating hybrid zone or outside
alldat.orn$loc <- ifelse(alldat.orn$cat == "Bull_ref", "Outside", "Hybrid zone") 

# Separate Bullock's
bullocks <- alldat.orn[which(alldat.orn$sp == "Bull"),]
```


Linear models
```{r H3 models, message = FALSE, warning = FALSE}
lm1 <- lm(B1 ~ date*loc, data=bullocks)
summary(lm1)
plot(lm1) 
vif(lm1) 
simulationOutput <- simulateResiduals(fittedModel = lm1, plot = F)
plot(simulationOutput)

lm2 <- lm(S9 ~ date*loc, data=bullocks)
summary(lm2)
plot(lm2) 
vif(lm2)
simulationOutput <- simulateResiduals(fittedModel = lm2, plot = F)
plot(simulationOutput)

lm3 <- lm(H3 ~ date*loc, data=bullocks)
summary(lm3)
plot(lm3) 
vif(lm3)
simulationOutput <- simulateResiduals(fittedModel = lm3, plot = F)
plot(simulationOutput)
```

#### Plots

1. Brightness
```{r Compare across bullocks hybrid zone - brightness, message = FALSE}
# Regression over time 
h3a <- ggplot(bullocks, aes(x = date, y = B1, shape = loc, color = loc)) +
  geom_point(size = 2) +
  stat_smooth(method = lm, aes(fill = loc), se = T) +
  theme_classic() +
  mytheme +
#  stat_fit_glance(method = "lm", 
#                        method.args = list(formula = y ~ x), size = 5, 
#                        aes(label = sprintf('R^2~"="~%.3f~~italic(p)~"="~%.3g',
#                                            stat(..r.squared..), stat(..p.value..))), 
#  parse = TRUE) + 
  labs(y = "Total brightness (B1)", x= "Collection date", color = "Location", 
       fill = "Location", shape = "Location") +
  scale_color_manual(values = pal3) +
  scale_fill_manual(values = pal3)

################
# black patches 
# not in manuscript 

bullblk <- alldat.blk[which(alldat.blk$sp == "Bull"),]

ggplot(bullblk, aes(x = date, y = B1)) +
  geom_point(size = 2) +
  stat_smooth(method = lm, se = T, col="black") +
  theme_classic() +
  mytheme +
#  stat_fit_glance(method = "lm", 
#                        method.args = list(formula = y ~ x), size = 5, 
#                        aes(label = sprintf('R^2~"="~%.3f~~italic(p)~"="~%.3g',
#                                            stat(..r.squared..), stat(..p.value..))),
#                        parse = TRUE) + 
  labs(y = "Total brightness (B1)", x= "Collection date") +
  scale_color_manual(values = pal3) +
  scale_fill_manual(values = pal3)
#ggsave("black_B1_time2.png", plot=last_plot(), width=200, height=125, units="mm", dpi=600, scale=T)
```

2. Chroma
```{r Compare across bullocks hybrid zone - chroma, message = FALSE}
h3b <- ggplot(bullocks, aes(x = date, y = S9, shape = loc, color = loc)) +
  geom_point(size = 2) +
  stat_smooth(method = lm, aes(fill = loc), se = T) +
  theme_classic() +
  mytheme +
#  stat_fit_glance(method = "lm",
#                        method.args = list(formula = y ~ x), size = 5, 
#                        aes(label = sprintf('R^2~"="~%.3f~~italic(p)~"="~%.3g',
#                                            stat(..r.squared..), stat(..p.value..))), 
#                  parse = TRUE) + 
  labs(y = "Carotenoid chroma (S9)", x = "Collection date", color = "Location", 
       fill = "Location", shape = "Location") +
  scale_color_manual(values = pal3) +
  scale_fill_manual(values = pal3)
```


3. Hue
```{r Compare across bullocks hybrid zone - hue, message = FALSE}
h3c <- ggplot(bullocks, aes(x = date, y = H3, shape = loc, color = loc)) +
  geom_point(size = 2) +
  stat_smooth(method = lm, aes(fill = loc), se = T) +
  theme_classic() +
  mytheme +
#  stat_fit_glance(method = "lm", 
#                        method.args = list(formula = y ~ x), size = 5, 
#                        aes(label = sprintf('R^2~"="~%.3f~~italic(p)~"="~%.3g',
#                                            stat(..r.squared..), stat(..p.value..))), 
#                        parse = TRUE) + 
  labs(y = "Hue (H3)", x = "Collection date", color = "Location", 
       fill = "Location", shape = "Location") +
  scale_color_manual(values = pal3) +
  scale_fill_manual(values = pal3)
```


Merge 
```{r Merge all plots, message = FALSE}
pg <- plot_grid(
  h3a + theme(legend.position="none"),
  h3b + theme(legend.position="none"),
  h3c + theme(legend.position="none"),
  align = 'vh',
  labels = c("A", "B", "C"),
  hjust = -1,
  nrow = 1, label_size = 16
)

leg <- get_legend(h3a + theme(legend.box.margin = margin(0,0,0,12)))

plot_grid(pg, leg, rel_widths = c(6, 0.8))

ggsave("Figure5.png", plot=last_plot(), width=600, height=225, units="mm", dpi=600, scale=T)
```


<br>


# Avian visual models

Using smoothed and averaged data: `allspec.orn.avg` and `allspec.blk.avg` 

## Noise-weighted distances with the Receptor Noise Model 

```{r avian visual models, message= FALSE}
vismod.orn <- vismodel(allspec.orn.avg,
  visual = "avg.uv", achromatic = "bt.dc", #blue tit double cone
  illum = "D65", relative = FALSE)
summary(vismod.orn)
head(vismod.orn)

# Get color distances
vismod.orn.dist <- coldist(vismod.orn,
  noise = "neural", achromatic = TRUE, n = c(1, 2, 2, 4),
  weber = 0.1, weber.achro = 0.1)


# bootstrap color distances
cate <- allcategory[-1] # get list made from above but remove wl from vector

vm.orn.dist <- bootcoldist(vismod.orn, by = cate, n = c(1,2,2,4), weber=0.1, achromatic = FALSE)
vm.orn.dist
```


```{r, fig.cap = "**Fig 6.** Chromatic contrasts (dS), vertical", message= FALSE}
# ggplot
# need to convert matrix into a usable data frame
vod <- as.data.frame(as.table(vm.orn.dist))
vod2 <- pivot_wider(vod, names_from = Var2, values_from = Freq)

# select comparisons
vod3 <- vod2 %>% 
  filter(Var1 == "Bull_hist-Bull_mod" | Var1 == "Balt_hist-Balt_mod" | 
         Var1 == "Balt_hist-Bull_hist" | Var1 == "Balt_mod-Bull_mod")

ggplot(vod3, aes(x=Var1, y=dS.mean)) +
  geom_errorbar(aes(ymin = dS.lwr, ymax = dS.upr), width=.3, 
                position = position_dodge(width=1), size=1) +
  geom_point(position = position_dodge(width=1), size=5) +
  theme_classic()+ 
  mytheme + 
  theme(text=element_text(family="sans")) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  coord_flip(clip="off") +
  labs(x=NULL, y = "Chromatic contrast (\u0394S)") +
  theme(panel.background = element_rect(fill = "transparent"), 
        axis.title.y = element_text(angle = 0, hjust = 0), # bg of the panel
        plot.background = element_rect(fill = "transparent", color = NA), # bg of the plot
        panel.grid.major = element_blank(), # get rid of major grid
        panel.grid.minor = element_blank(), # get rid of minor grid
        legend.background = element_rect(fill = "transparent"), # get rid of legend bg
        legend.box.background = element_rect(fill = "transparent"))+
  scale_x_discrete(limits = c("Balt_mod-Bull_mod", "Balt_hist-Bull_hist", 
                              "Balt_hist-Balt_mod", "Bull_hist-Bull_mod"), 
                   labels = c("Interspecific contemporary", "Interspecific historic",
                              expression(paste("Intraspecific ", italic("Icterus galbula"))),
                              expression(paste("Intraspecific ", italic("Icterus bullockii"))))) +
  geom_text(x=4.5, y=0.2, inherit.aes = F, label = "Centroid comparison", 
            check_overlap = T, hjust =1, fontface="bold", size=7)

ggsave("chromatic_contrast.png", plot = last_plot(), width = 200, height = 80, 
       units = "mm", dpi = 300,  bg = "transparent")

ggplot(vod3, aes(x=Var1, y=dS.mean)) +
  geom_errorbar(aes(ymin = dS.lwr, ymax = dS.upr), width=.3, 
                position = position_dodge(width=1), size=1) +
  geom_point(position = position_dodge(width=1), size=5) +
  theme_classic()+ 
  mytheme + 
  theme(text=element_text(family="sans")) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  coord_flip(clip="off") +
  labs(x=NULL, y = "Chromatic contrast (\u0394S)") +
  theme(panel.background = element_rect(fill = "transparent"), 
        axis.title.y = element_text(angle = 0, hjust = 0), # bg of the panel
        plot.background = element_rect(fill = "transparent", color = NA), # bg of the plot
        panel.grid.major = element_blank(), # get rid of major grid
        panel.grid.minor = element_blank(), # get rid of minor grid
        legend.background = element_rect(fill = "transparent"), # get rid of legend bg
        legend.box.background = element_rect(fill = "transparent"))+
  scale_x_discrete(limits = c("Balt_mod-Bull_mod", "Balt_hist-Bull_hist", 
                              "Balt_hist-Balt_mod", "Bull_hist-Bull_mod"), 
                   labels = c("Contemporary Baltimore vs Bullock's",
                              "Historic Baltimore vs Bullock's",
                              "Historic vs contemporary Baltimore",
                              "Historic vs contemporary Bullock's"
                              )) +
  geom_text(x=4.5, y=0.2, inherit.aes = F, label = "Centroid comparison", 
            check_overlap = T, hjust =1, fontface="bold", size=7)

ggsave("chromatic_contrast.png", plot = last_plot(), width = 200, height = 80, 
       units = "mm", dpi = 300,  bg = "transparent")
```
